MINOS Handover Plots

### 2024-02-06 minos/validation/handovers.Rmd
ncars fully working and in handovers. needs some tweaks as underpredicting zeros.

```{r}
raw.ncars <- raw.dat %>%
  dplyr::select(pidp, time, ncars) %>%
  group_by(time, ncars) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  dplyr::select(pidp, time, ncars) %>%
  group_by(time, ncars) %>%
  count() %>%
  mutate(source = 'baseline_output')

>>>>

```{r}
raw.ncars <- raw.dat %>%
  dplyr::select(pidp, time, ncars) %>%
  select(ncars >= 0) %>%
  group_by(time, ncars) %>%
  count() %>%
  mutate(source = 'final_US')

base.ncars <- base.dat %>%
  dplyr::select(pidp, time, ncars) %>%
  select(ncars >= 0) %>%
  group_by(time, ncars) %>%
  count() %>%
  mutate(source = 'baseline_output')
